Exponential Family Markets for Information Aggregation

### 2014-02-12 WriteUp/maxentpredmkts.tex
fixed a typo

Notice that Lemma~\ref{thm:growth} only required that the market state to which the trader moves, be representable as a convex combination of the current market state and his belief. This means that the result holds for exponential utility traders aiming to maximize their utility. In this case, the trader who moves the market state can expect his profit to be positive and at least $\frac{1}{a}D_{T}(\theta,\htheta)$ where $a$ is the exponential utility parameter. When the cost function is adjusted with a liquidity parameter as $C_{l}(\theta)=(1/l) C(l\theta)$ as described in Section \ref{sec:exputil},  the trader receives an expected payoff of at least $\frac{1}{a} D_{T}(\theta'/l,\htheta)$.

>>>>

Notice that Lemma~\ref{thm:growth} only required that the market state to which the trader moves, be representable as a convex combination of the current market state and his belief. This means that the result holds for exponential utility traders aiming to maximize their utility. In this case, the trader who moves the market state can expect his profit to be positive and at least $\frac{1}{a}D_{T}(\theta,\htheta)$ where $a$ is the exponential utility parameter. When the cost function is adjusted with a liquidity parameter as $C_{l}(\theta)=(1/l) C(l\theta)$ as described in Section \ref{sec:exputil},  the trader receives an expected payoff of at least $\frac{1}{a} D_{T}(l\theta',\htheta)$.
